Cover Letter

### 2023-10-22 manuscript.qmd
Update

---
format:
  docx:
    reference-doc: template.docx
bibliography: hellp.bib
csl: bmj.csl
---

@@

This systematic review was conducted following the methodological standards of Cochrane Handbook. [@cochrane2023] We prospectively registered the protocol in Open Science Platform. The full text of the protocol is available in an open access registry and as an online supplementary file. We reported the review using the Preferred Reporting Items for Systematic reviews and Meta-Analyses (PRISMA) standards. [@page2021]

@@

A comprehensive literature search was initially conducted on September 20, 2023. We did not impose language or other restrictions on any of the searches. We searched bibliographic databases (Cochrane Central Register of Controlled Trials (CENTRAL), MEDLINE/PubMed) and citation indexes (Web of Science and Scopus). The detailed exact strategy adapted for each database is provided in a supplementary file and is also available in an open access registry document. We peer-reviewed the search strategy and further tested it with a set of known relevant, 'gold standard', reports. We also searched clinical trial registries (ClinicalTrials.gov and the World Health Organization International Clinical Trials Registry Platform) to identify ongoing trials. We finally searched reference lists and explored the cited-by logs of identified studies and previously published reviews.

@@

We assessed the risk of bias for the included RCTs contributing results to our outcomes using the RoB 2 tool. The overall risk of bias for all study results per outcome are available in supplementary file 2.

@@

Six trials (449 women) reported maternal death. The risk ratio (RR) was 0.77 (95% confidence intervals (CI) 0.25 to 2.38, @fig-md). The effect of any corticosteroid vs placebo or no treatment is uncertain. We downgraded the certainty of the evidence to very low due to extremely serious imprecision, @tbl-grade.

The subgroup analysis did not show significant differences among groups whether by the timing of corticosteroid administration (test for subgroup differences P = 0.79) or by the type of corticosteroid (test for subgroup differences P = 0.60).

Sensitivity analysis to explore robustness of pooled estimate for maternal death, using outcome data from trials with a low risk of bias showed results similar to primary analysis with a RR 0.87 (95% CI 0.26 to 2.92) or by including studies with zero events with RR 0.79 (95% CI 0.27 to 2.32).

@@

# Supplemental file

Supplemental file 1: Systematic review protocol

Supplemental file 2: PRISMA checklist

Supplemental file 3: Detailed search strategy

Supplemental file 4: Data and analysis code

# Figure legend

>>>>

---
format: docx
bibliography: hellp.bib
csl: bmj.csl
---

@@

This systematic review was conducted following the methodological standards of Cochrane Handbook. [@cochrane2023] We prospectively registered the protocol in Open Science Platform. The full text of the protocol is available in an open access registry and as an online as [Supplemental file 1] . We reported the review using the Preferred Reporting Items for Systematic reviews and Meta-Analyses (PRISMA) standards. [@page2021] The full checklist is available as [Supplemental file 2].

@@

A comprehensive literature search was initially conducted on September 20, 2023. We did not impose language or other restrictions on any of the searches. We searched bibliographic databases (Cochrane Central Register of Controlled Trials (CENTRAL), MEDLINE/PubMed) and citation indexes (Web of Science and Scopus). The detailed exact strategy adapted for each database is provided in [Supplemental file 3] and is available as an open access registry document. We peer-reviewed the search strategy and further tested it with a set of known relevant, 'gold standard', reports. We also searched clinical trial registries (ClinicalTrials.gov and the World Health Organization International Clinical Trials Registry Platform) to identify ongoing trials. We finally searched reference lists and explored the cited-by logs of identified studies and previously published reviews.

@@

We assessed the risk of bias for the included RCTs contributing results to our outcomes using the RoB 2 tool. The overall risk of bias for all study results per outcome are available in [Supplemental file 4].

@@

Six trials (449 women) reported maternal death. The risk of bias for the included RCTs contributing results to maternal death ia available in the [Supplemental file 4]. The risk ratio (RR) was 0.77 (95% confidence intervals (CI) 0.25 to 2.38, @fig-md). The effect of any corticosteroid vs placebo or no treatment is uncertain. We downgraded the certainty of the evidence to very low due to extremely serious imprecision, @tbl-grade.

The subgroup analysis did not show significant differences among groups whether by the timing of corticosteroid administration (test for subgroup differences P = 0.79) or by the type of corticosteroid (test for subgroup differences P = 0.60) ([Supplemental file 4]).

Sensitivity analysis to explore robustness of pooled estimate for maternal death, using outcome data from trials with a low risk of bias showed results similar to primary analysis with a RR 0.87 (95% CI 0.26 to 2.92) or by including studies with zero events with RR 0.79 (95% CI 0.27 to 2.32) ([Supplemental file 4]).

@@

## Supplemental files

### Supplemental file 1

### Supplemental file 2

### Supplemental file 3

### Supplemental file 4

## Figure legend
